Pangenome graph layout by HOGWILD! path-guided stochastic gradient descent

### 2022-09-21 manuscript/main.tex
update affiliations

\author{ %[Heumos, \textit{et~al}.]{
  Simon Heumos\,$^{1,2 \dagger}$,
  Andrea Guarracino\,$^{3 \dagger}$,
  Sven Nahnsen\,$^{1,2}$,
  Pjotr Prins\,$^4$,
  and Erik Garrison\,$^{4 *}$
}

\affil{\small$^1$Quantitative Biology Center (QBiC), University of Tübingen, Tübingen 72076, Germany \\
  $^2$ Biomedical Data Science, Department of Computer Science, University of Tübingen , Tübingen 72076, Germany \\ 
  $^3$Genomics Research Centre, Human Technopole, Milan 20157, Italy \\
  $^4$
  Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, TN 38163, USA \\
  $^\ast$To whom correspondence should be addressed. \\
  $^\dagger$Contributed equally.}

>>>>

\author{ %[Heumos, \textit{et~al}.]{
  Simon Heumos\,$^{1,2 \dagger}$,
  Andrea Guarracino\,$^{3 \dagger}$,
  Jan-Niklas Manuel Schmelzle\,$^{4,5}$,
  Jiajie Li\,$^{4,5}$,
  Sven Nahnsen\,$^{1,2}$,
  Pjotr Prins\,$^6$,
  and Erik Garrison\,$^{6 *}$
}

\affil{\small$^1$Quantitative Biology Center (QBiC), University of Tübingen, Tübingen 72076, Germany \\
  $^2$Biomedical Data Science, Department of Computer Science, University of Tübingen , Tübingen 72076, Germany \\ 
  $^3$Genomics Research Centre, Human Technopole, Milan 20157, Italy \\
  $^4$Department of Computer Engineering, School of Computation, Information and Technology (CIT), Technical University of Munich, Munich 80333, Germany \\
  $^5$School of Electrical and Computer Engineering, Cornell University, Ithaca, NY 14853, USA \\
  $^6$Department of Genetics, Genomics and Informatics, University of Tennessee Health Science Center, Memphis, TN 38163, USA \\
  $^\ast$To whom correspondence should be addressed. \\
  $^\dagger$Contributed equally.}
